### 2017-07-07 implementation.tex
Impl.

At the top-level, \tool runs a loop that pics an unverified
transaction and progressively strengthens its isolation level until it
passes the verification. If the selected data store provides
serializable isolation level, and if the program is sequentially
corred, then the verification is guaranteed to succeed. Within the
loop, the \tool first computes the various rely relations needed for
verification ($R$, $\R_l$, and $\R_c$). It then traverses the AST of a
transaction, applying the inference rules to construct a state
tansformer, check its stability, and weaken it ($\stabilize{\cdot}$)
if it is not stable. The result of traversing the transaction's AST is
therefore a stable state transformer ($\F$), which is then checked
against the transaction's stated guarantee ($G$). If the check passes,
then the guarantee is verified to check if it preserves the invariant
$I$. The successful result from both the checks results in the
transaction being certified correct under the current choice of its
isolation level. Succesful verification of all transactions concludes
the top-level execution, returning the inferred isolation levels as
its output.

@@

\textbf{Set functions} SQL's \C{SELECT} query admits projections of
record fields, and also application of auxiliary functions such as
\C{MAX} and \C{MIN}. For example, \C{SELECT MAX(ol\_o\_id) FROM
Order\_line WHERE $\ldots$}. We admit such extensions as set functions
in our DSL (e.g., \C{project}, \C{max}, \C{min}), and axiomatize their
behavior. For instance:
\begin{smathpar}
\begin{array}{lcl}
  s_2 \;=\;\C{project}\,s_1\,(\lambda z.~e) & \Leftrightarrow &
  \forall y.~y\in s_2 \Leftrightarrow  \exists(x \in s_1).~y = [x/z]e\\
  x \;=\; \C{max}\,s & \Leftrightarrow & x \in s \conj \forall(y \in
  s).~y\le x\\
\end{array}
\end{smathpar}
There are however certain set functions that

>>>>

At the top-level, \tool runs a loop that pics an unverified
transaction and progressively strengthens its isolation level until it
passes the verification. If the selected data store provides
serializable isolation level, and if the program is sequentially
corred, then the verification is guaranteed to succeed. Within the
loop, the \tool first computes the various rely relations needed for
verification ($R$, $\R_l$, and $\R_c$). It then traverses the AST of a
transaction, applying the inference rules to construct a state
tansformer, check its stability, and weaken it ($\stabilize{\cdot}$)
if it is not stable. The result of traversing the transaction's AST is
therefore a state transformer ($\F$) that is stable w.r.t $R_l$, which
is also stabilized against $\R_c$ (using $\stabilize{\cdot}$), and
then checked against the transaction's stated guarantee ($G$). If the
check passes, then the guarantee is verified to check if it preserves
the invariant $I$. The successful result from both the checks results
in the transaction being certified correct under the current choice of
its isolation level. Succesful verification of all transactions
concludes the top-level execution, returning the inferred isolation
levels as its output.

@@

\textbf{Set functions} SQL's \C{SELECT} query admits projections of
record fields, and also application of auxiliary functions such as
\C{MAX} and \C{MIN}. For example, \C{SELECT MAX(ol\_o\_id) FROM
Order\_line WHERE $\ldots$}. We admit such extensions as set functions
in our DSL (e.g., \C{project}, \C{max}, \C{min}), and axiomatize their
behavior. For instance:
\begin{smathpar}
\begin{array}{lcl}
  s_2 \;=\;\C{project}\,s_1\,(\lambda z.~e) & \Leftrightarrow &
  \forall y.~y\in s_2 \Leftrightarrow  \exists(x \in s_1).~y = [x/z]e\\
  x \;=\; \C{max}\,s & \Leftrightarrow & x \in s \conj \forall(y \in
  s).~y\le x\\
\end{array}
\end{smathpar}
There are however certain set functions whose behavior cannot be
completely axiomatized in FOL. These include \C{sum}, \C{count} etc.
For them we admit imprecise axiomatization in form certain lemmas on
these functions.

\textbf{Annotation Burden} \tool significantly reduces the annotation
burden in verifying a weakly isolated transactions by eliminating the
need to annotate intermediary assertions and loop invariants.
Guarantees ($G$) and invariants ($I$), however, still need to be
provided. Alternatively, a weakly isolated transaction $T$ can be
verified against the generic serializability condition, to eliminate
the need for any annotation. In this mode, \tool first infers the
transformer $\F_{SER}$ of $T$ without considering any interference,
which then becomes its guarantee ($G$). Doing likewise for every
transaction results in a rely relation ($R$) that includes $\F_{SER}$
of every transaction. The verification can now proceed as usual. The
result of this verification is an assignment of (possibly weak)
isolation levels to transactions which guarantees serializability of
all executions.
